Who introduced this bug? \\ It may not have been caused by the previous commit!

### 2016-02-01 paperMSR.tex

For that, we had to analyze the lines involved in the bug fix and in the \emph{parent} commit of the bug fix commit, being sure that the lines were added, inserted or modified in the previous commit. We refer to \emph{parent} commit as the last commit that was edited to produce the subsequent state of the file. We do this process to be sure that we are looking the correct change, because some times although the commit added many lines, if you look the code before the commit you can check that some of the lines added was there, and in that case, it is a false positive where the previous commit did not cause the bug. \grex{Gema, puedes aclarar este parrafo? Que es el "parent" commit? Es lo mismo que el previous commit? Es la primera vez que hablamos de el. Quizas sea buena idea que lo reformules en castellano, porque ahora mismo es criptico}\gema{el parent commit es el ultimo commit que se hizo en el fichero antes de que se realizase el que arreglo el error, por tanto lo que hago usar diff y blame en el commit parent y en el commit que arregla el error para saber que lineas se han cambiado y que commit las cambio), y despues hago lo mismo con el commit previo y el commit parent del previo para saber que en realidad en ese momento se produjo el cambio. En el gerrit nos dan esa info como se puede ver en la figura~\ref{fig:parent}}

\grex{Sigue sin quedarme clara cual es la relacion entre el parent commit y el previous commit (mira que yo pensaba que eran lo mismo)... podriamos dar una definicion?}

\begin{figure}[ht]
\centering
\includegraphics[height=2cm]{parent.png}
\label{fig:parent}       % Give a unique label
\caption{Information in Gerrit.\grex{contar que se ve en la figura}}
\end{figure}

@@

With our results we can identify which ones are real changes that introduced the bug, and this could be useful to improve the accuracy of those tools developed to prevent bugs. Also, the software developers stand to benefit from identifying where the bug was inserted, improving their methodology.
%How to plan to apply the knowledge in a way that can benefit software engineers.
%What are the anticipated contributions of the work?  How will you evaluate them to demonstrate usefulness?

A final field in our future work concerns the full automation of the methodology could developer an automatic classifier base on the idea that not all the previous commit injected the bug. Another interesting investigation could perform the same empirical study in a project with a community less active, to can prove if our idea is fulfill in other projects.\grex{Puedes aclarar esto, porfa? En castellano si quieres}
\gema{Si, la idea es realizar el mismo estudio pero con otro projecto que no sea OpenStack, porque en realidad OpenStack esta evolucionando continuamente. Y para poder demostrar que en realidad la idea se cumple en todos los projectos, deberiamos analizar un projecto que sea mas 'estable' y en el que la API no se este cambiando continuamente }

>>>>

For that, we had to analyze the lines involved in the bug fix and in the \emph{parent} commit of the bug fix commit, being sure that the lines were added, inserted or modified in the previous commit. We refer to \emph{parent} commit as the commit that modified any line of code in the file before the fix-bug commit, in contrast to the \emph{previous} commit where the modified lines were the same than in the fix-bug commit. It should be noted that those lines modified in the parent commit do not have to be the ones that have been modified in the bug-fix.
Figure~\ref{fig:parentgerrit} contains a snapshot of the information provided by Gerrit, where the link to the parent commit(s) can be found, that corresponds to the bug-fix shown in~\ref{fig:1}. As can be seen, the previous commit (\textit{31f08423}) in Figure~\ref{fig:1} is different from the parent commit displayed in Figure~\ref{fig:parentgerrit} (\textit{db7fc59ebc}).

We do this process to be sure that we are looking the correct change, because sometimes although the commit added many lines, if you look the code before the commit you can check that some of the lines added was there, and in that case, it is a false positive where the previous commit did not cause the bug.

%\grex{Gema, puedes aclarar este parrafo? Que es el "parent" commit? Es lo mismo que el previous commit? Es la primera vez que hablamos de el. Quizas sea buena idea que lo reformules en castellano, porque ahora mismo es criptico}\gema{el parent commit es el ultimo commit que se hizo en el fichero antes de que se realizase el que arreglo el error, por tanto lo que hago usar diff y blame en el commit parent y en el commit que arregla el error para saber que lineas se han cambiado y que commit las cambio), y despues hago lo mismo con el commit previo y el commit parent del previo para saber que en realidad en ese momento se produjo el cambio. En el gerrit nos dan esa info como se puede ver en la figura}

%\grex{Sigue sin quedarme clara cual es la relacion entre el parent commit y el previous commit (mira que yo pensaba que eran lo mismo)... podriamos dar una definicion?}  
%\gema{EL parent commit es el ultimo commit que toco alguna linea del fichero antes de que se realizase el fix bug commit, pero las lineas que toco el commit parent no tienen porque contener ningun bug. Mientras que el commit previo es la ultima modificacion que se hizo en aquellas lineas que ha tocado el bug-fix.Estaría bien dar una definicion por si no se ve claro}

\begin{figure}[ht]
\centering
\includegraphics[height=2cm]{parent.png}
\caption{Information about the bug as displayed by Gerrit.}
\label{fig:parentgerrit}       % Give a unique label
\end{figure}

@@

With our methodology we have identifie which are real changes that introduced the bug, and this could be useful to improve the accuracy of those tools developed to prevent bugs. Also, the software developers stand to benefit from identifying where the bug was inserted, improving their methodology.
%How to plan to apply the knowledge in a way that can benefit software engineers.
%What are the anticipated contributions of the work?  How will you evaluate them to demonstrate usefulness?

A final field of future work could be concerned with the full automation of the methodology, developing  an automatic classifier based on the idea that not all the previous commits inject the bug. \grex{mejorar este parrafo.}

Another interesting investigation could perform the same empirical study on a project with a less active community, to prove if our idea is fulfill in other projects. So, for projects that do not evolve as rapidly as OpenStack, e.g., those with a more stable API, could offer completely different results even if applying the same analysis methodology used in this paper.
